%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Benjamin Gluck} \\ \vspace{1pt}
    \small 614-980-8891 $|$ \href{mailto:b.gluck132@gmail.com}{\underline{b.gluck132@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ben-gluck}{\underline{linkedin.com/in/ben-gluck}} $|$
    \href{https://github.com/glucko}{\underline{github.com/glucko}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Ohio State University}{Expected Graduation: May 2027}
      {Honors B.S. in Computer Science \& Engineering}{GPA: 4.0}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Web Development Intern}{June 2024 -- August 2024}
      {Netsteady}{Hilliard, OH}
      \resumeItemListStart
        \resumeItem{Developed an internal timeclock system and dashboard used by 20+ employees using PHP, MySQL, and jQuery.}
        \resumeItem{Designed a digital signage API and dashboard for handling 30+ smart TVs, saving \$600+ in monthly fees.}
        \resumeItem{Created 5+ web forms that integrated with automation systems to streamline ticketing and support requests.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Solutions Intern}{June 2022 -- August 2022}
      {OSA Technology Partners}{Columbus, OH}
      \resumeItemListStart
        \resumeItem{Earned Sophos Firewall, Central Endpoint and Server, and Central Overview Engineer certificates.}
        \resumeItem{Earned JumpCloud Core Certificate, gaining skills to onboard employees and manage user access and directories.}
        \resumeItem{Onboarded employees of JobsOhio through Zoom into new management software.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Fencing Tracker} $|$ \emph{Python, Flask, SQLAlchemy, Jinja2, Bootstrap}}{Spring 2023}
          \resumeItemListStart
            \resumeItem{Developed a web app to track fencing matches and tournaments for use at my fencing club.}
            \resumeItem{Designed an interface to easily accept, display, and update data, improving scoring and record-keeping.}
            \resumeItem{Utilized an SQLite database with Flask to analyze matches and easily accept user input.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AgreeToDisagree} $|$ \emph{JavaScript, TalkJS API, Bootstrap}}{Summer 2022}
          \resumeItemListStart
            \resumeItem{Developed a web app designed to connect people with differing viewpoints through bonding activities.}
            \resumeItem{Implemented a login system to improve ease of use, sustain conversations, and store user preferences.}
            \resumeItem{Implemented the TalkJS API for a user-friendly chat system, improving communication and accessibility.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Fairy Chess} $|$ \emph{Python, Pygame}}{Summer 2023}
          \resumeItemListStart
            \resumeItem{Developed a Pygame chess app with a graphical user interface.}
            \resumeItem{Implemented responsive controls and interactive visuals for an enhanced player experience.}
            \resumeItem{Utilized object-oriented programming to create extendable classes for custom piece creation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------Volunteering-----------
\section{Volunteering}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cohort Member}{August 2022 - August 2023}
      {Wexner Service Corps}{Columbus, OH}
      \resumeItemListStart
        \resumeItem{Sorted magazines to be distributed to low-income communities to foster passion for reading.}
        \resumeItem{Volunteered at an elder care center, talking to residents with dementia and other illnesses to offer them comfort.}
        \resumeItem{Assisted Habitat for Humanity with yard work and house maintenance to help families in need.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  
%-----------Awards-----------
\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{First Place}{: Ohio State University High School I/O Cybersecurity Challenge (50+ participants)} \\
     \textbf{Second Place}{: Phillips Exeter Academy Hackathon (100+ participants)} \\
     \textbf{Second Place}{: Hathaway Brown Byte (70+ participants)} \\
     \textbf{Third Place}{: 2022 Ohio High School Fencing Championship} \\
     \textbf{Third Place}{: 2023 Ohio High School Fencing Championship} \\
     \textbf{Schholarships}{: OSU Maximus, Governor's Merit} \\
    }}
 \end{itemize}

  
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, PHP, Java, HTML/CSS, JavaScript, SQL} \\
     \textbf{Frameworks \& Libraries}{: Flask, Django, SQLAlchemy, Pygame, Pandas, Bootstrap, jQuery} \\
     \textbf{Developer Tools}{: Linux, Git, Markdown, VS Code} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
